A Survey of Real-Time Strategy Game AI\\ Research and Competition in StarCraft

### 2013-07-24 survey.tex
Adding Michal work

% CBR:
Also falling into the machine-learning category, a significant group of researchers has explored case-based reasoning (CBR) \cite{Aamodt94CBR} approaches for strategic decision making. For example Aha et al. \cite{LTW} used CBR to perform dynamic plan retrieval in the Wargus domain. Hsieh and Sun \cite{HsiehS08} based their work on Aha et al.'s CBR model \cite{LTW} and used StarCraft replays to construct states and building sequences (``build orders''). Finally, Schadd et al. \cite{SchaddBS07} applied a CBR approach to opponent modeling through hierarchically structured models of the opponent behavior and they applied their work to the Spring RTS game (a ``Total Annihilation'' clone).

@@

>>>>

% CBR:
Also falling into the machine-learning category, a significant group of researchers has explored case-based reasoning (CBR) \cite{Aamodt94CBR} approaches for strategic decision making. For example Aha et al. \cite{LTW} used CBR to perform dynamic plan retrieval in the Wargus domain. Hsieh and Sun \cite{HsiehS08} based their work on Aha et al.'s CBR model \cite{LTW} and used StarCraft replays to construct states and building sequences (``build orders''). Schadd et al. \cite{SchaddBS07} applied a CBR approach to opponent modeling through hierarchically structured models of the opponent behavior and they applied their work to the Spring RTS game (a ``Total Annihilation'' clone). Finally, \v{C}ertick\'{y} et al. \cite{certicky2013cbr} used CBR to build their army based on the opponent's army composition and they pointed the importance of a proper scouting for better results.

@@

% WALLING
Walling is the act of intentionally placing buildings at the entrance of your base to block the path and to prevent the opponent's units from getting inside. This technique is used by human StarCraft players to survive early aggression and earn time to train more units. \v{C}ertick\'{y} solved this constraint satisfaction problem using Answer Set Programming (ASP) \cite{certicky2013wallin}.
